PubCrawl: A Publication Search Engine

### 2012-05-17 report/paper.tex
few updates
Combine introduction and related work

\documentclass[12pt]{article}
\setcounter{secnumdepth}{2}

\title{PubCrawl: A Publication Search Engine}
\author{Frank Li (frankli@mit.edu) \\
Abhishek Sarkar (aksarkar@mit.edu)\\
Manasi Vartak (mvartak@mit.edu)}
\date{May 16, 2012}

@@

A primary source of information for computer science researchers are published
papers from conference proceedings and journals. However, there are simply too
many papers in published in too many venues to keep track of. While experienced
researchers are typically versed in the famous and influential papers of their
respective fields, they may be less familiar with other areas that might still
be needed for their work. Less experienced researchers and students may have
even less or no knowledge of the relevant papers of a subject.

To address this issue, researchers have create paper search engines, such as
Google Scholar and CiteseerX. However, the ranking process for these systems is
largely privately maintained. In this paper, we investigate the process of
ranking in the academic papers setting. An understanding of this is important
to create a better search system.

To do this, we designed PubCrawl, a paper search engine, as a testing bed for
ranking mechanisms. In building PubCrawl, we used Apache Lucene for text
indexing to measure a paper’s relevance to a query, and an adaptation of
PageRank on the papers citation graph for weighting a paper’s importance.
Currently all papers in the Association of Computing Machinery (ACM) Digital
Library database have been processed. A simple web user interface is provided,
where users can input queries and weights for what attributes they feel is most
important, to tune the result rankings to fit what they feel is most
appropriate. The top papers are returned, with hyperlinks to the papers’ ACM
homepage.

In this report, we detail the design of PubCrawl and investigate the effects of
many of its features. We conduct a user study to compare the performance of our
ranking system versus other current systems.

\section{Related Work}

There are a few paper search engines currently in existence, such as CiteseerX
and Google Scholar. Their ranking process is largely maintained privately, but
several characteristics of both are described in this section.

CiteseerX's data set is scraped from the web by a crawler, and processed in an
automated fashion. This has provided CiteseerX with wide and largely hands-off
coverage of papers. However, due to the purely automated approach used and the
heterogeneity in data representation on the web, the data collected contains
errors and missing information. For example, the crawler has mistaken the wrong
string for the title of a number of papers. This leads to some errors in the
processing of both the paper data and queries.

Google Scholar also operates with a crawler, and exhibits some of the same
dirty data issues as CiteseerX. Additionally, Google Scholar has been shown to
be heavily influenced by citation count, which may be inappropriate for some
user queries.

@@

\section{Acknowledgments}
\null

>>>>

\documentclass[12pt]{article}
\setcounter{secnumdepth}{2} 
\title{PubCrawl: A Publication Search Engine}
\author{Frank Li (frankli@mit.edu) \\
Abhishek Sarkar (aksarkar@mit.edu)\\
Manasi Vartak (mvartak@mit.edu)}
\date{May 16, 2012}

@@

A primary source of information for computer science researchers are published
papers from conference proceedings and journals. As the number of papers and
venues increases, the ability to quickly find papers relevant to a given topic
becomes more important. In particular, researchers want search engines which
return important papers.

There are several existing search engines for academic papers, most prominently
Google Scholar, \citeseer, and Microsoft Academic Search. Google Scholar uses a
proprietary algorithm which combines several approaches. However, researchers
have partially reverse engineered it \cite{beel09a, beel09b}. In particular,
the algorithm is biased towards highly cited papers, which should highly rank
important papers in the standard literature. However, the bias
will also make the algorithm miss more recent influential papers. Researchers
also uncovered several weaknesses in Google's automatic processing of documents
which could allow authors to game search rankings \cite{beel10}.

\citeseer\ is primarily an automatic citation indexing system \cite{giles98,
  lawrence99, li06}. The system crawls the web and processes documents which
appear to be academic papers. This approach produces a large corpus of noisy
data, which hurts the performance of its ranking algorithm. Also,
\citeseer\ does not make use of the citation data it processes in its ranking
algorithm.

Microsoft Academic Search is a relatively new search engine designed to compete
with Google Scholar. It too uses a proprietary algorithm which combines several
features, and shows the same weakness to ranking optimization as Scholar.

Here, we present PubCrawl, a system built to test ranking algorithms for
searching academic papers. The system searches over the complete ACM Digital
Library. We use Apache Lucene to index documents and estimate relevance and
PageRank to estimate importance. The system provides a web interface using the
Django web framework backed by a Postgres database. Users can input queries and
relative weights for matches in various sections of the document as well as the
PageRank.

@@

\section{Acknowledgments}

\bibliography{refs}{}
\bibliographystyle{acm}
